\documentclass[verdana]{moderncv}

\usepackage[scale=0.8]{geometry}
\moderncvstyle{classic}
\moderncvcolor{blue}

\firstname{David}
\lastname{Kleiven}
\title{Curriculum Vitae}
\address{Edgar B. Schieldropsvei 100B}{7021 Trondheim}
\mobile{93060916}
\email{davidkleiven446@gmail.com}

\begin{document}
\makecvtitle

\section{Education}
\cvitem{2011-Present}{Master in applied physics, NTNU (Norwegian University of Science and Technology}
\cvitem{2010-2011}{Military service, H.M. King's Guard Music and Drill Company}
\cvitem{2007-2010}{General studies at Skeisvang vgs.}

\section{Experience}
\cventry{2015 - Present}{Technical Student at CERN}{}{}{}{Working on a project
concerning determination of the damage limits of the Large Hadron Collider (LHC) superconducting magnets
due to beam impact. Typical tasks include taking part in the design of experimental
setups, simulating interactions between charged particles and matter and
performing damage tests on critical components of the LHC superconducting magnets.}
\cventry{2015}{Summer internship at Silicon Labs}{}{}{}{Implementing bluetooth
support for microcontrollers and extending the amount of available examples for
Silicon Labs' microcontrollers on the Mbed platform.}
\cventry{2014}{Summer internship at W{\"a}rtsil{\"a}}{}{}{}{Building graphics for cargo ship control system applications.} 
\cventry{2014}{Summer internship at Polytec}{}{}{}{Research assistant on a project concerning functional materials.}
\cventry{2013}{Summer internship at Gassco}{}{}{}{Statistical analysis of gas prognosis.}
\cventry{2011-2013}{Teaching assistant in various courses at NTNU}{}{}{}{Supervising a group of about 20 students in exercise classes.}

\section{Computer Skills}
\cvitem{Programming}{C/C++, Fortran, MATLAB, Python, Perl}
\cvitem{Word processing}{\LaTeX, MS Office, Open office}

\section{Languages}
\cvitem{Norwegian}{Native speaker}
\cvitem{English}{Fluent}
\cvitem{German}{Basic}
\cvitem{French}{Basic}

\section{References}
\cvitem{}{Provided on request.}
\end{document}

